\SW: I. Crowd-sourcing the Discovery of Gravitational Lenses

### 2015-05-14 doc/sw-system.tex
Corrected 'users' to 'volunteers' throughout, #207

A screenshot of the \SW classification interface (CI) is shown in
\Fref{fig:screenshot}. The CI is the centrepiece of the \SW website,
\texttt{http://spacewarps.org}; the web application is written in coffeescript,
css and html and follows the general design of others written by the Zooniverse
team.\footnote{The \SW web application code is open source and can be accessed
from \texttt{https://github.com/zooniverse/Lens-Zoo}.  The project was renamed
during development to avoid the question of  who ``Len'' is.} The focus of the
CI is a large display of a pre-prepared PNG image of the ``subject'' being
inspected. When the image is clicked on by the volunteer, a marker symbol
appears at that position.  Several markers can be placed, and they can be
removed by the user if they change their mind.

@@

\begin{minipage}{\linewidth}
  \begin{minipage}[t]{0.47\linewidth}
    \begin{minipage}{0.46\linewidth}
      \centering\includegraphics[width=\linewidth]{ASW0000fgj_gri.pdf}
    \end{minipage}\hfill
    \begin{minipage}{0.50\linewidth}
      \centering\includegraphics[width=\linewidth]{ASW0000fgj_stage1_trajectory.pdf}
    \end{minipage}
  \end{minipage}\hfill
  \begin{minipage}[t]{0.47\linewidth}
    \begin{minipage}{0.46\linewidth}
      \centering\includegraphics[width=\linewidth]{ASW0003j2s_gri.pdf}
    \end{minipage}\hfill
    \begin{minipage}{0.50\linewidth}
      \centering\includegraphics[width=\linewidth]{ASW0003j2s_stage1_trajectory.pdf}
    \end{minipage}
  \end{minipage}
\end{minipage}
\caption{Illustrative examples of
false negatives (blue) and false positives (red) from the classification of
the \SW$-$\cfhtls training set. The trajectory plot for each of the 4 subjects is
shown to the right of its image. Lefthand panels show the most common types of
trajectories: short step random walks resulting from no high skill classifiers
viewing the subject. The righthand panels show examples where higher skill
classifiers have been involved, causing random walks with longer step lengths
(top) and catastrophic mis-classifications (bottom right). Note that both these
subjects were {\it very nearly} detected but didn't quite reach the threshold
set (marked by the blue dashed line). Insets for the false
negatives show the lens feature. The inset for the lower righthand panel shows
where most users believed a lens was located. There is no corresponding inset
for the lower left panel because no particular feature stood out to users.
Instead, users clicked many different features.}
\label{fig:discuss:performance:trajectories}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

The false positives show similar behaviour, for example in the bottom lefthand
panel of the figure. As well as subjects being ``unlucky'' in this way, there
are two less common failure modes associated with mistakes made by higher skill
users, illustrated in the righthand column of the figure. In the false negative
subject shown in the top right-hand panel, several high skill classifiers update
the subject upwards in log probability by some way each time, but other,
comparable skill classifiers mis-classify the system to lower probability.   The
trajectory looks like a random walk, but with bigger steps; this particular
subject came very close to crossing the detection  threshold three times, but
didn't quite make it. The bottom right-hand panel shows an example of a final,
apparently rare, failure mode: we see some short-step random walk behaviour,
followed by a mis-classification by a very high skill ``expert'' classifier
after 20 classifications that promotes the subject to high probability.

@@

Some of  the mistakes made by reasonably high skill classifiers working at high
speed could have perhaps been corrected by those classifiers themselves, had
they had access to a ``go back'' option. While clearly enabling error reduction,
we might worry about such a mechanism enabling classifiers to have a guess, then
go and read the \Talk discussion, and then return to the classification
interface to change their mind to agree with the forum. In fact, this is already
possible on the current interface -- and indeed, it is not obvious that such
correlations would necessarily lead to poorer system performance. There may well
also be effects on user confidence; it may be that encouraging this sort of
checking would result in increased and not necessarily productive caution. This
could be tested by presenting a fraction of the volunteers with a version of the
site that actively suggested that they take this approach, and then tracking the
relative performance of ``collaborative'' classifications compared with
independent ones. We leave the exploration of this to further work.

@@

There are (at least) two ways in which we might increase the numbers of
high-contribution volunteers for larger projects in future. The first is
simply to increase the total crowd size, and hope that a similar fraction of
volunteers make large contributions. Greater exposure of the website to the
public through mass media would help. Another option is to advertise the
project to new groups of volunteers by translating the website into other
languages (something which is now supported by the Zooniverse). A
multi-lingual user base would come with its own set of challenges, especially
in terms of volunteers' continuing training and interactions on \Talk.

The second way to scale up the number of high contribution classifiers is to
increase the rate at which new volunteers become dedicated volunteers. Based on
feedback from the wider \SW community, this could potentially be achieved
through closer collaboration with the science team. It is also possible that
dynamically assigning subjects on the basis of the volunteer's skill could act
as an incentive to some volunteers to increase their contribution, although any
such approach would need to take into account the need to optimise not only for efficiency but also for the most interesting or pleasurable volunteer experience; a solution which gave every volunteer a very uniform experience, for example, is unlikely to succeed even if it appears optimally efficient.  Reducing the
rate at which new volunteers lose interest could also play a role. Anecdotally,
it seems fairly common for new volunteers to be wary of classifying at all, for
fear of introducing errors. Better explanation of how their early
classifications are analyzed could help assuage these fears:
\Sref{sec:results:crowd} shows that effectively down-weighting new users'
classifications (by setting their agents' initial confusion matrix elements to
those of a random classifier) leads to best performance, a result which should
be of some comfort to the nervous volunteer.

>>>>

A screenshot of the \SW classification interface (CI) is shown in
\Fref{fig:screenshot}. The CI is the centrepiece of the \SW website,
\texttt{http://spacewarps.org}; the web application is written in coffeescript,
css and html and follows the general design of others written by the Zooniverse
team.\footnote{The \SW web application code is open source and can be accessed
from \texttt{https://github.com/zooniverse/Lens-Zoo}.  The project was renamed
during development to avoid the question of  who ``Len'' is.} The focus of the
CI is a large display of a pre-prepared PNG image of the ``subject'' being
inspected. When the image is clicked on by the volunteer, a marker symbol
appears at that position.  Several markers can be placed, and they can be
removed by the classifier if they change their mind.

@@

\begin{minipage}{\linewidth}
  \begin{minipage}[t]{0.47\linewidth}
    \begin{minipage}{0.46\linewidth}
      \centering\includegraphics[width=\linewidth]{ASW0000fgj_gri.pdf}
    \end{minipage}\hfill
    \begin{minipage}{0.50\linewidth}
      \centering\includegraphics[width=\linewidth]{ASW0000fgj_stage1_trajectory.pdf}
    \end{minipage}
  \end{minipage}\hfill
  \begin{minipage}[t]{0.47\linewidth}
    \begin{minipage}{0.46\linewidth}
      \centering\includegraphics[width=\linewidth]{ASW0003j2s_gri.pdf}
    \end{minipage}\hfill
    \begin{minipage}{0.50\linewidth}
      \centering\includegraphics[width=\linewidth]{ASW0003j2s_stage1_trajectory.pdf}
    \end{minipage}
  \end{minipage}
\end{minipage}
\caption{Illustrative examples of
false negatives (blue) and false positives (red) from the classification of
the \SW$-$\cfhtls training set. The trajectory plot for each of the 4 subjects is
shown to the right of its image. Lefthand panels show the most common types of
trajectories: short step random walks resulting from no high skill classifiers
viewing the subject. The righthand panels show examples where higher skill
classifiers have been involved, causing random walks with longer step lengths
(top) and catastrophic mis-classifications (bottom right). Note that both these
subjects were {\it very nearly} detected but didn't quite reach the threshold
set (marked by the blue dashed line). Insets for the false
negatives show the lens feature. The inset for the lower righthand panel shows
where most volunteers believed a lens was located. There is no corresponding inset
for the lower left panel because no particular feature stood out to the
classifiers. Instead, the volunteers clicked many different features.}
\label{fig:discuss:performance:trajectories}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

The false positives show similar behaviour, for example in the bottom lefthand
panel of the figure. As well as subjects being ``unlucky'' in this way, there
are two less common failure modes associated with mistakes made by higher skill
volunteers, illustrated in the righthand column of the figure. In the false negative
subject shown in the top right-hand panel, several high skill classifiers update
the subject upwards in log probability by some way each time, but other,
comparable skill classifiers mis-classify the system to lower probability.   The
trajectory looks like a random walk, but with bigger steps; this particular
subject came very close to crossing the detection  threshold three times, but
didn't quite make it. The bottom right-hand panel shows an example of a final,
apparently rare, failure mode: we see some short-step random walk behaviour,
followed by a mis-classification by a very high skill ``expert'' classifier
after 20 classifications that promotes the subject to high probability.

@@

Some of  the mistakes made by reasonably high skill classifiers working at high
speed could have perhaps been corrected by those classifiers themselves, had
they had access to a ``go back'' option. While clearly enabling error reduction,
we might worry about such a mechanism enabling classifiers to have a guess, then
go and read the \Talk discussion, and then return to the classification
interface to change their mind to agree with the forum. In fact, this is already
possible on the current interface -- and indeed, it is not obvious that such
correlations would necessarily lead to poorer system performance. There may well
also be effects on volunteer confidence; it may be that encouraging this sort of
checking would result in increased and not necessarily productive caution. This
could be tested by presenting a fraction of the volunteers with a version of the
site that actively suggested that they take this approach, and then tracking the
relative performance of ``collaborative'' classifications compared with
independent ones. We leave the exploration of this to further work.

@@

There are (at least) two ways in which we might increase the numbers of
high-contribution volunteers for larger projects in future. The first is
simply to increase the total crowd size, and hope that a similar fraction of
volunteers make large contributions. Greater exposure of the website to the
public through mass media would help. Another option is to advertise the
project to new groups of volunteers by translating the website into other
languages (something which is now supported by the Zooniverse). A
multi-lingual userbase would come with its own set of challenges, especially
in terms of volunteers' continuing training and interactions on \Talk.

The second way to scale up the number of high contribution classifiers is to
increase the rate at which new volunteers become dedicated volunteers. Based on
feedback from the wider \SW community, this could potentially be achieved
through closer collaboration with the science team. It is also possible that
dynamically assigning subjects on the basis of the volunteer's skill could act
as an incentive to some volunteers to increase their contribution, although any
such approach would need to take into account the need to optimise not only for efficiency but also for the most interesting or pleasurable volunteer experience; a solution which gave every volunteer a very uniform experience, for example, is unlikely to succeed even if it appears optimally efficient.  Reducing the
rate at which new volunteers lose interest could also play a role. Anecdotally,
it seems fairly common for new volunteers to be wary of classifying at all, for
fear of introducing errors. Better explanation of how their early
classifications are analyzed could help assuage these fears:
\Sref{sec:results:crowd} shows that effectively down-weighting new volunteers'
classifications (by setting their agents' initial confusion matrix elements to
those of a random classifier) leads to best performance, a result which should
be of some comfort to the nervous volunteer.
